---
title: "Netflix Data Analysis"
output:
  pdf_document: default
  html_document: default
date: "2022-09-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Installing Libraries:

Installing all necessary libraries.

```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(naniar)
library(forcats)
library(wordcloud)
library(tm)
library(SnowballC)
library(RColorBrewer)
library(tidytext)
library(tinytex)
```

# Used head function to look at top 6 rows of data and read the data in.

Reading csv file and looking at the first rows.

```{r}
library(readxl)
netflix = read.csv("netflix_titles.csv")
head(netflix)
```

# Summary

Used glimpse and summary functions to look at the summary of the data.

```{r}
glimpse(netflix)
```

```{r}
summary(netflix)
```

## Used separate function to split date added column intop 2 columns

We separate the year from the date column within our data.

```{r}
netflix = netflix %>% separate(date_added,c("date_added", "year_added"), sep = ",")
```

```{r}
netflix = netflix %>% separate(listed_in, c("Category1", "Category2", "Category3"), sep = ",")
```

### Country column analysis

Cleaning the NA values from the dataset.

```{r}
library(dplyr)
#Check how many NA values we have in the column
netflix = netflix %>% 
  mutate(country = ifelse(country == "", NA, country ))
 netflix %>% count(is.na(netflix$country), sort = TRUE)
 
 country <- drop_na(netflix, country) 
```

## We see top countries in Netflix based on the number of movies and tv shows

Using the dplyr package we arrange the data by looking at the top 25 countries that produce movies or tv shows.

```{r}
country %>% group_by(country) %>% count(country, type) %>% arrange((desc(n))) %>% head(25)
```

### Data Visualization

Movies and tv shows over the years.

```{r}
ggplot(netflix, mapping = aes(x=release_year, fill = type)) +
geom_histogram(color = "black", binwidth=2)+
labs(title="Releases by Year")
```

```{r}
netflix %>%
count(is.na(netflix$country), sort = TRUE)
country_release <- drop_na(netflix, country)
country_release %>%
    count(country, sort = TRUE) %>%
    group_by(country) %>%
    head(25) %>%
    ggplot(aes(x=reorder(country, n), y=n, fill=country)) +
    geom_col(show.legend = FALSE) +
    labs(x="Sum of Movies and TV Shows Frequency", y="Movies and TV Shows Rleased", title="Top 25 Countries on Netflix") +
    coord_flip() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
    geom_label(aes(label=n), show.legend=FALSE) +
    scale_y_continuous(expand = c(0, 0), limits = c(0, 3000))
```

# Netflix TV shows rating by Type

In this graph, we can observe that TV-MA rating is the most popular in netflix.

```{r}
netflix %>%
 filter(!(rating %in% c("74 min", "84 min", "66 min", ""))) %>%
 ggplot() +
  aes(x = rating, fill = rating) +
  geom_bar() +
  scale_fill_hue(direction = 1) +
  labs(x = "Rating", y = "Count", title = "Rating by Type") +
  theme_minimal() +
  facet_wrap(vars(type)) +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
desc_words_m <- netflix %>% select(type, show_id, description) %>%
  filter(type == "Movie") %>% 
    unnest_tokens(word, description) %>%
    anti_join(stop_words)
count_word <- desc_words_m %>%
   count(word, sort = TRUE)
wordcloud(words = count_word$word,  
          freq = count_word$n, 
          min.freq = 50,  
          max.words = nrow(count_word), 
          random.order = FALSE,  
          rot.per = 0.1,  
          colors = brewer.pal(8, "Dark2"))
```

The wordcloud above shows the most common word searched in netflix.
